### 2021-04-16 input/figaddA.tex
meow

  \draw (-\X + 5pt, 0) -- (0 - 5pt, 0); %% a - b

  \draw (0 +5pt, 0) -- (\X -5pt, 0); %% b - c

  \draw (0, 0 - 5pt) -- (0, \Y + 5pt); %% d - b

  \draw (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d

>>>>

  \draw (-\X + 5pt, 0) --
  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{2}
  (0 - 5pt, 0); %% a - b

  \draw (0 +5pt, 0) --
  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{1}
  (\X -5pt, 0); %% b - c

  \draw (0, 0 - 5pt) --
  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{1}
  (0, \Y + 5pt); %% d - b

  \draw (\X + 3pt, 0 - 5pt) --
  node[shape=circle, draw, fill=white, inner sep=0.5px, font=\footnotesize]{3}
  (0 + 5pt, \Y - 3pt); %% c - d

### 2021-04-16 input/proposal.tex
meow

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from \Process
  $i$ to \Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
  \pi_{ij}[m+1] \rangle \in E$.
\end{definition}

@@

\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
  Consistent partitioning where each \process can \texttt{Add} and
  \texttt{Del}ete its partition at any time requires
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, and
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{corollary}

@@

Algorithm~\ref{algo:adddelundo} provides the instructions that
implement dynamic consistent partitioning:
\begin{inparaenum}[(i)]
\item \label{algo:most} most of the time, it propagates $\alpha$'s and
  $\delta$'s when the partitions allow it;
\item \label{algo:sometimes} sometimes, it detects possible
  inconsistent partitioning and
\item \label{algo:solves}solves it using propagation trees (as opposed
  to propagation graphs);
\item \label{algo:competition} when required, it triggers competitions
  among neighboring partitions.
\end{inparaenum}
While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
stale notifications, (\ref{algo:competition}) tackle the eventual
delivery of the best up-to-date partitions.

\begin{algorithm}
  \input{input/algoadddelundo.tex}
  \caption{\label{algo:adddelundo}Dynamic partitioning by \Process $p$.}
\end{algorithm}

@@

Vectors of versions also allow each \process to detect possible last
win order violations. Upon possible inconsistency, the detecting
\process must remove all $\alpha$ messages originating from it, as
labeled by IV in Figure~\ref{fig:proofB}. Contrarily to delete
operations, this applies to a sub-partition of the current partition,
and cannot rely on local counters to
operate. Algorithm~\ref{algo:adddelundo} implements this behavior by
piggybacking paths in messages. Paths guarantee that such $\delta$
messages apply to all and only $\alpha$'s that followed an identical
path. $\delta$'s propagate in the propagation tree rooted at the
detecting \process. Local states of \processes remain unchanged, but
paths in messages monotonically grow. In turns, $\alpha$ and $\delta$
cannot follow each other in an infinite loop, for a \process knows when
it already received a forwarded a message (see
Lines~\ref{line:notloopingA} and \ref{line:notloopingB}).

@@

\begin{algorithm}
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}Dynamic partitioning by \Process $p$ in dynamic networks.}
\end{algorithm}

@@

\vfill

\TODO{spacing}

\newpage

>>>>

\begin{definition}[Edge infrastructure]
  An edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from \Process
  $i$ to \Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
  \pi_{ij}[m+1] \rangle \in E$.
\end{definition}

@@

\begin{corollary}[\label{theo:dcp}\underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
  Consistent partitioning where each \process can \texttt{Add} and
  \texttt{Del}ete its partition at any time requires
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, and
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{corollary}

@@

Algorithm~\ref{algo:ascast} provides the instructions that
implement dynamic consistent partitioning:
\begin{inparaenum}[(i)]
\item \label{algo:most} most of the time, it propagates $\alpha$'s and
  $\delta$'s when the partitions allow it;
\item \label{algo:sometimes} sometimes, it detects possible
  inconsistent partitioning and
\item \label{algo:solves}solves it using propagation trees (as opposed
  to propagation graphs);
\item \label{algo:competition} when required, it triggers competitions
  among neighboring partitions.
\end{inparaenum}
While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
stale notifications, (\ref{algo:competition}) tackle the eventual
delivery of the best up-to-date partitions.

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process $p$ in static networks.}
\end{algorithm}

@@

Vectors of versions also allow each \process to detect possible last
win order violations. Upon possible inconsistency, the detecting
\process must remove all $\alpha$ messages originating from it, as
labeled by IV in Figure~\ref{fig:proofB}. Contrarily to delete
operations, this applies to a sub-partition of the current partition,
and cannot rely on local counters to
operate. Algorithm~\ref{algo:ascast} implements this behavior by
piggybacking paths in messages. Paths guarantee that such $\delta$
messages apply to all and only $\alpha$'s that followed an identical
path. $\delta$'s propagate in the propagation tree rooted at the
detecting \process. Local states of \processes remain unchanged, but
paths in messages monotonically grow. In turns, $\alpha$ and $\delta$
cannot follow each other in an infinite loop, for a \process knows when
it already received a forwarded a message (see
Lines~\ref{line:notloopingA} and \ref{line:notloopingB}).

@@

\begin{algorithm}
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process $p$ in dynamic networks.}
\end{algorithm}

@@
